\documentclass[margin,line]{res}


\oddsidemargin -.5in
\evensidemargin -.5in
\textwidth=6.0in
\itemsep=0in
\parsep=0in

\newenvironment{list1}{
  \begin{list}{\ding{113}}{%
      \setlength{\itemsep}{0in}
      \setlength{\parsep}{0in} \setlength{\parskip}{0in}
      \setlength{\topsep}{0in} \setlength{\partopsep}{0in} 
      \setlength{\leftmargin}{0.17in}}}{\end{list}}
\newenvironment{list2}{
  \begin{list}{$\bullet$}{%
      \setlength{\itemsep}{0in}
      \setlength{\parsep}{0in} \setlength{\parskip}{0in}
      \setlength{\topsep}{0in} \setlength{\partopsep}{0in} 
      \setlength{\leftmargin}{0.2in}}}{\end{list}}

\usepackage{color}
\usepackage[bookmarks=false]{hyperref}
\definecolor{darkblue}{rgb}{0.0,0.0,0.3}
\hypersetup{colorlinks,breaklinks,
            linkcolor=darkblue,urlcolor=darkblue,
            anchorcolor=darkblue,citecolor=darkblue}

\begin{document}

\name{Wang, Dingquan \vspace*{.1in}}

\begin{resume}
\section{\sc Contact Information}
\vspace{.05in}
\begin{tabular}{@{}p{2.5in}p{0.55in}p{2in}}
186 Claremont Ave., Apt 2S, & {\it Mobile:}& (917)680-9648 \\  
New York, NY, 10025& {\it E-mail:}& wddabc@gmail.com\\
\end{tabular}

\section{\sc Courses}
Natural Language Processing (A+), Machine Learning (A+), Advanced Machine Learning (A+)
\section{\sc Education}

{\bf Columbia University}, New York, US\\
{\em The Fu Foundation School of Engineering \& Applied Science} 
\begin{list1}
\item[] Masters, Computer Science, September, 2012- Decemeber, 2013, GPA: 3.95/4.0\\
\begin{list2}
\vspace*{-4mm}
\item Adviser: Dr. Rebecca J. Passonneau and Prof. Michael Collins 
\end{list2}
\end{list1}
\vspace*{-4mm}
{\bf Shanghai Jiao Tong University}, Shanghai, China\\
{\em Computer Science and Technology(ACM Honored Class)} 
\vspace*{-.0in}
\begin{list1}
\item[] B.S., Engineering, July, 2011, Major GPA: 3.74/4.3
\begin{list2}
\vspace*{.05in}
\item Dissertation Topic:  ``Intent Based Query Clustering on User Logs'' 
\item Adviser: Prof. Yong Yu 
\end{list2}
\end{list1}
\section{\sc Honors and Awards} 
MSTA Fellowship of Columbia University \hfill{Spring, 2013}\\
Microsoft Excellent Internship Award \hfill{April,2011}\\
Microsoft Young Fellowship Award(3/1000), \hfill{May, 2010}\\
Excellent Academic Scholarship, Shanghai Jiao Tong University, Class B(Three times) \hfill{2007--2010}\\
\vspace*{-2.5mm}

\section{\sc Projects}
{\bf Research Assistant, Center for Computational Learning Systems,  Columbia University}\\
\hspace*{3pt}\hfill {\bf January, 2013 - December, 2013}
\begin{list1}
\item[] Bloomberg project for dependency parsing \hfill{September, 2013 - }
\item[] Manhole events prediction on Manhattan power grid \hfill{June, 2013 - December, 2013}
\item[] Semantic feature representation to capture news impact \hfill{January, 2013 - June, 2013}\\
\item[]	Sentiment analysis for citing sentence \hfill{September, 2012-Decemeber, 2012}
\end{list1}
\vspace*{-4mm}
{\bf Research Assistant, Apex Data\&Knowledge Management Lab, Shanghai Jiao Tong University} \hfill {\bf June, 2009 - June, 2012}\\
\vspace*{-4mm}
\begin{list1}
\item[] Content and advertisement-sensitive PageRank\hfill {September, 2009 - June, 2011}
\item[] Query clustering by user intents \hfill{February, 2011 - June, 2011}
\item[] Restricted Boltzmann Machine for Collaborative Filtering \hfill{ March, 2010 - June, 2010}
\item[] PASCAL challenge: LSHTC\footnote {\href{http://lshtc.iit.demokritos.gr/}{Large Scale Hierarchical Text Classification}} \hfill{July, 2009 - November, 2009}
\end{list1}
\section{\sc Professional Experience}
\begin{list1}
\item[] {\bf MSTA}:Advanced Machine Learning by Prof. Tony Jebara. \hfill{Spring, 2013}
\item[] {\bf TA}:Machine Learning by Prof. Tony Jebara. \hfill{Fall, 2012}
\item[] {\bf Full-time internship}: Web Data Management Group, Microsoft Research Asia. \hfill { July, 2011 - September, 2011 and July, 2010 - February, 2011}
\item[] {\bf TA}: Mathematics in Computer Science by Prof. John E. Hopcroft.\hfill {Spring, 2012}
\item[] {\bf Verifier}: Chinese version of ``Foundations of Semantic Web Technologies'' \hfill {Spring, 2011}
\item[] {\bf TA}: Computer Organization Lab., 08 ACM Honored Class. \hfill {Spring, 2010}
\end{list1}

\section{\sc Computer Skills} 
{\bf OS, Tools and IDEs}: Windows, Linux, Mac, Latex, Gnuplot, Vim, Eclipse\\
{\bf Programming Skills}: C, C++, C\#, Java, Matlab, Python, Perl, R

\end{resume}
\end{document}
